Concurrent Programming with CXL

### 2020-06-20 book/paper.tex
Latest

\section*{Exercices}
\begin{enumerate}
\item Add an assertion that demonstrates that at most three
Italian philosophers are eating at the same time?
\item Implement a test program that checks to see that
the solution allows more than one Italian philosopher to eat at the same time?
\end{enumerate}

>>>>

\section*{Exercices}
\begin{enumerate}
\item Add an assertion that demonstrates that at most three
Italian philosophers are eating at the same time?
\item Implement a test program that checks to see that
the solution allows more than one Italian philosopher to eat at the same time?
\item Figure~\ref{fig:qsort} shows an iterative implementation of the Qsort
algorithm, and Figure~\ref{fig:qsorttest} an accompanying test program.
Note that it uses a shared variable \texttt{a} containing the array to be
sorted and a shared variable \texttt{todo} containing the ranges of the
array that need to be sorted (initially the entire array).
Re-using as much of this code as you can, implement a parallel version of
this.  You should not have to change the methods \texttt{swap}, \texttt{partition},
or \texttt{sortrange} for this.  Create \texttt{NWORKERS} ``worker processes''
that should replace the \texttt{qsort} code.  Each worker loops until \texttt{todo}
is empty and sorts the ranges that it finds until then.  The \texttt{main}
process needs to wait until all workers are done.  Use a semaphore for this:
the \texttt{main} process should use \texttt{P} to wait for each
worker to terminate.  After that it should check if the array is sorted and a
permutation of the original array.
\end{enumerate}

\begin{figure}
\begin{code}
\VerbatimInput[xleftmargin=5mm,numbers=left]{code/qsort.cxl}
\end{code}
\caption{[qsort.cxl] Iterative qsort() implementation.}
\label{fig:qsort}
\end{figure}

\begin{figure}
\begin{code}
\VerbatimInput[xleftmargin=5mm,numbers=left]{code/qsorttest.cxl}
\end{code}
\caption{[qsorttest.cxl] Test program for Figure~\ref{fig:qsort}.}
\label{fig:qsorttest}
\end{figure}
